Higher-Order unification for free!

### 2024-07-01 paper/main.tex
(sec 8) add ref Higher-Order Logic Programming as Constraint Logic Programming

The main difference is that we cannot implement \hrun since it is
the runtime of the programming language. In particular the runtime iterates
\Ue, but \hstep also needs to check links for \progress. Luckily Elpi extends
$\lambda$Prolog with constraints (suspended goals) and
Constraint Handling Rules (CHR) to operate on them~\cite{TASSI_2019,fruehwirth2017constraint}.
An important design choice is that constraints are suspended on a user
computed list of unification variables, and are resumed \emph{as soon as one of them
is assigned}, before any other existing goal is considered. In turn this
property allows for a timely activation of links that grants~\fullref{prop:fidelity}.
For brevity we only provide two pseaudo-code snippets. The first one depicts
how \linketa are suspended or make \progress.

>>>>

The main difference is that we cannot implement \hrun since it is
the runtime of the programming language. In particular the runtime iterates
\Ue, but \hstep also needs to check links for \progress. Luckily Elpi extends
$\lambda$Prolog with constraints (suspended goals) and
Constraint Handling Rules (CHR) to operate on them~\cite{TASSI_2019,fruehwirth2017constraint}.
Similarly to \cite{pfenning1993}, a constraint is a delayed unification problems
suspended on a list of variables and is resumed \emph{as soon as one of these variable
is assigned}, before any other existing goal is considered. We point out that
we extend \cite{pfenning1993}, since we delay not only \notllambda unification problems, 
but also those problems that are still in \maybeeta.  
In turn link activation grants~\fullref{prop:fidelity}.
For brevity we only provide two pseaudo-code snippets. The first one depicts
how \linketa are suspended or make \progress.
